Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-08-31 paper/main.tex
add summary of method to intro of results

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.
The ``parahippocampal place area'' (PPA) in the human ventral visual stream
exhibits increased hemodynamic activity correlated with the perception of
landscape photos compared to faces or objects.
% AV, AD: operationalization
Here, we investigate the perception of scene-related, spatial information embedded in two naturalistic stimuli.
%
The same 14 participants were watching a Hollywood movie and listening to its
audio-description as part of the open-data resource \textit{studyforrest.org}.
% auditory localizer?
%in order to explore if a naturalistic auditory narrative could be used to
%localize a ``visual area''.  GLM
We model hemodynamic activity based on annotations of selected stimulus
features,
% VIS
and compare results to a block-design visual localizer.
% no refs in abstract (probably)
%\citep{sengupta2016extension}.  results: group AV
On a group level, increased activation correlating with visual spatial information
occurring in the movie is overlapping with a traditionally localized PPA.
% results: group AD
Activation correlating with semantic spatial information occurring in the
audio-description is more restricted to the anterior PPA.
% results: individual AD
On an individual level, we find significant bilateral activity in the PPA
of nine individuals and unilateral activity in one individual.
% conclusion: generalizability
Results suggest that activation in the PPA generalizes to spatial information
embedded in a movie and an auditory narrative, and may
% conclusion: PPA has subregions
call for considering a functional subdivision of the PPA.  \end{abstract}

@@

\todo[inline]{Summarize some methods here?}

% study goal
We investigated if spatial information embedded in two naturalistic stimuli
correlates with increased hemodynamic activity in the PPA.
% group level
On a group average level, we compared results from whole-brain general linear
model (GLM) analyses of
the movie and the audio-description to a traditional visual localizer
\citep{sengupta2016extension}.
% individual level
For each individual, we also compared the activation pattern from naturalistic
auditory stimulation to the individual PPA localization with a block-design
stimulus.
% NeuroVault
Unthresholded $Z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts co-registered to the group-template (MNI152
space) can be found at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.
% reference to supplemental material
Additional analyses of the robustness of the results presented here are
available in the Supplementary Information.

>>>>

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.
The ``parahippocampal place area'' (PPA) in the human ventral visual stream
exhibits increased hemodynamic activity correlated with the perception of
landscape photos compared to faces or objects.
% AV, AD: operationalization
Here, we investigate the perception of scene-related, spatial information embedded in two naturalistic stimuli.
%
The same 14 participants were watching a Hollywood movie and listening to its
audio-description as part of the open-data resource \textit{studyforrest.org}.
% auditory localizer?
%in order to explore if a naturalistic auditory narrative could be used to
%localize a ``visual area''.
We model hemodynamic activity based on annotations of selected stimulus
features,
% VIS
and compare results to a block-design visual localizer.
% no refs in abstract (probably)
%\citep{sengupta2016extension}.  results: group AV
On a group level, increased activation correlating with visual spatial information
occurring in the movie is overlapping with a traditionally localized PPA.
% results: group AD
Activation correlating with semantic spatial information occurring in the
audio-description is more restricted to the anterior PPA.
% results: individual AD
On an individual level, we find significant bilateral activity in the PPA
of nine individuals and unilateral activity in one individual.
% conclusion: generalizability
Results suggest that activation in the PPA generalizes to spatial information
embedded in a movie and an auditory narrative, and may
% conclusion: PPA has subregions
call for considering a functional subdivision of the PPA.  \end{abstract}

@@

\todo[inline]{I tried to keep the summary of methods short and use a pretty
similar phrasing; still, I wouldn't get the result section and read the Method
section and tables there while reading the results\dots. Most important imo is
to link the Tables (Events + Contrasts) and explain that there is that ``primary
contrast'' thing.}

% study goal
We investigated if spatial information embedded in two naturalistic stimuli
correlates with increased hemodynamic activity in the PPA.
%
Based on an annotation of cuts in the movie and an annotation of speech spoken
by the audio-description's narrator, we selected events in both stimuli that
should correlate with the perception of spatial information and contrasted them
with events that should not (or to a less degree) correlate with non-spatial
perception (see Table~\ref{tab:events}).
% from supplementals
In order to test the robustness of our approach, we created multiple linear
model (GLM) $t$-contrasts for the movie and audio-description (see
Table~\ref{tab:contrasts}).
% subjectively assessed balance
For each stimulus, we chose a primary contrast for result presentation (marked
with an asterisk in the table) based on a subjectively assessed balance of how
well the averaged events within categories represent spatial and non-spatial
information, and the number of events in the stimulus.
% group level
On a group average level, we here report results from whole-brain analyses of
the movie's and the audio-description's primary contrasts and compare these
results to a traditional visual localizer \citep{sengupta2016extension}.
% individual level
For each individual, we also compare the activation pattern from naturalistic
auditory stimulation to the individual PPA localization with a block-design
stimulus.
% reference to supplementals
An evaluation of the results' robustness across all created contrasts on a group
average level is provided in the Supplementary Information (see
Figure~\ref{fig:stability-slices-volsurf}).
% NeuroVault
Unthresholded $Z$-maps of all contrasts on a group average level as well as
individual results of the primary $t$-contrasts co-registered to the
group-template (MNI152 space) can be found at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.
